```{r}
#install.packages("plspm")
library(plspm)
library(tidyverse)

setwd("../Team-6/")
df <- readxl::read_xlsx("Data/mendeley_aps/ACSI_Data_2015.xlsx")

# Define the list of blocks (or observed variables) for each latent variable
blocks = list(
            # Customer Expectations
            # OVERALLX, CUSTOMX, WRONGX
            
            6:8,
            # Perceived Loyalty
            # OVERALLQ, CUSTOMQ, WRONGQ
            9:11,
            # Perceived Value
            # PQ, QP
            12:13,
            # Customer Satisfaction
            # SATIS, CONFIRM, IDEAL
            3:5,
            # Customer Complaints
            # COMP, HANDLE
            14:15,
            # Customer Loyalty
            # REPUR, HIGHPTOL, LOWPTOL
            16:18
            )
lapply(blocks, function(block) names(df)[block])

```
Define Relationships:

Customer Expectations -> Perceived Quality
Perceived Quality -> Perceived Value
Customer Expectations -> Perceived Value

Perceived Value -> Customer Satisfaction
Perceived Quality -> Customer Satisfaction
Customer Expectations-> Customer Satisfaction 

Customer Satisfaction -> Customer Complaints
Customer Satisfaction -> Customer Loyalty
Customer Complaints -> Customer Loyalty
```{r}
inner = matrix(c(
# Expectations maps to Quality, Value, Satisfaction
  0, 1, 1, 1, 0, 0,
# Quality maps to Value, Satisfaction
  0, 0, 1, 1, 0, 0,
# Value maps to Satisfiaction
  0, 0, 0, 1, 0, 0,
# Satisfaction maps to complaints, loyalty
  0, 0, 0, 0, 1, 1,
# complaints maps to loyalty
  0, 0, 0, 0, 0, 1,
# Loyalty maps to none
  0, 0, 0, 0, 0, 0
), nrow = 6, ncol = 6, byrow = FALSE)
inner
```
```{r}
# Each block is formative (latent variable is formed by the observed variables)

modes = rep("B", 6)
```
```{r}
latent = c( "Customer Expectations",
            "Perceived Loyalty",
            "Perceived Value",
            "Customer Satisfaction",
            "Customer Complaints",
            "Customer Loyalty")
            
```

```{r}
# Run the PLS-PM model
plspm_model <- df %>% 
    plspm(.,path_matrix = inner, 
          
          blocks = blocks, 
          modes = modes,
          scaling=T,
)


# Print out the results
print(plspm_model)
```

